WIDS 2024 Final Project

### 2024-01-08 Code/R FIle.qmd
added names for state specific exploratory graphs

#### Graphing Full State Data

>>>>

#### Graphing Full State Data
##### For facets, use best judgement if by state, decade, year, or region
##### maybe make all states light grey and just choose outline outlier states and maybe regional averages

##### Party by state and year
##### Min Wage by state and year (include fed (facet or use by decades where necessary)
##### Adjusted Min Wage by state and year (include adjusted fed (facet or use by decades where necessary)
##### Union employment, CB employment, and full employment (facet by decade)
##### percent union and percent collective bargaining
